---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# image-montages

* A quick and experimental look at creating an image from a montage arrangement of a second image - using `{magick}`
  * This is **super slow** and seems to use a lot of memory on my laptop (especially if the image is made larger)

```{r warning=FALSE, message=FALSE}
library(magick)
library(tidyverse)
```

* Read the 'main' background image resized to 100 px wide
```{r}
i <- 
  image_read('https://i5.walmartimages.com/asr/105ad9f3-4b18-461e-b158-8f95d7281ec5_1.d436e8e8146bae6cf1bcb2848be5676d.jpeg') %>% 
  image_resize("100x")

image_ggplot(i)
```

* Store the width and height of the background image (px)
```{r}
info <- image_info(i)
w <- info$width
h <- info$height
```

* Set the width of the second image used as the 'pixel'
* Read the second 'pixel' image and crop to fill a square (pix_size x pix_size)
```{r}
pix_size <- 25

i_pix <- 
  image_read('https://www.pngjoy.com/pngm/880/10347686_doom-guy-doom-guy-transparent-png.png') %>% 
  image_convert(colorspace = "gray") %>% 
  image_resize(paste0(pix_size, "x", pix_size, "^")) %>% 
  image_crop(paste0(pix_size, "x", pix_size), gravity = "center")

image_ggplot(i_pix)
```

* Iterate through every pixel in background image, creating a composite image of the pixel and the 'pixel' image
* Compose type of 'HardLight' was found by trial and error - there may be a better ('proper') compose type to use for this
  * **This is REALLY slow and memory intensive**
```{r fig.width=10, fig.height=10}
composites <-
  i %>% 
  image_raster() %>%
  pull(col) %>% 
  lapply(function(x) image_composite(image_colorize(i_pix, opacity=100, color=x), 
                                     composite_image = i_pix, 
                                     operator = "Hardlight")) %>% 
  image_join() %>% 
  image_montage(geometry = geometry_size_pixels(pix_size, pix_size),
                tile = paste0(w, "x", h)) 

composites
```

* Zoom in 
```{r}
composites %>% image_crop("300x300", gravity = "center") %>% image_ggplot()
```

